\bf Range Analysis for the IonMonkey JavaScript engine

### 2012-04-30 project-writings/paper.tex
Talk about ionmonkey

\section{Implementation}
%% XXX: TODO

>>>>

\section{Implementation}
%% XXX: TODO
The IonMonkey compiler is somewhat loosely based on LLVM, in that it is an
imperative SSA compiler. IonMonkey takes the bytecode used by the SpiderMonkey
Javascript interpreter and compiles it to native code. Optimistic type
specialization is used, and if type assumptions fail, then execution ``bails
out'' to the interpreter.

IonMonkey has two intermediate languages. There is a ``Middle Intermediate
Representation'' which encompasses higher-level constructs such as lambdas,
objects, and strings. A variety of optimizations are performed, and then the
code is lowered to a ``Lower Intermediate Representation'' used for register
allocation and code generation.

While the ECMA specification for Javascript requires that all numbers behave as
double-precision floating point values, for performance reasons JIT compilers
represent numbers as 32-bit integers when possible. However, since doubles can
represent larger values than integers, operations must be guarded against
overflow.  Our range analysis pass eliminates overflow checks when operations
can be proven not to overflow.
